CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds

### 2017-10-11 AISTATS2018/cake_aistats2018.tex
Version before major revision

\newacronym{CME}{CME}{conditional mean embedding}
\newacronym{MCE}{MCE}{multiclass conditional embedding}
\newacronym{CEN}{CEN}{conditional embedding network}
\newacronym{RKHS}{RKHS}{reproducing kernel Hilbert space}
\newacronym{SVM}{SVM}{support vector machine}
\newacronym{SVC}{SVC}{support vector classifier}
\newacronym{GP}{GP}{Gaussian process}
\newacronym{GPs}{GPs}{Gaussian processes}
\newacronym{GPC}{GPC}{Gaussian process classifier}
\newacronym{KRR}{KRR}{kernel ridged regressor}
\newacronym{RLSC}{RLSC}{regularized least squares classification}
\newacronym{ERM}{ERM}{empirical risk minimization}
\newacronym{MMD}{MMD}{maximum mean discrepancy}
\newacronym{RCB}{RCB}{Rademacher complexity bound}
\newacronym{OVA}{OVA}{one versus all}
\newacronym{CNN}{CNN}{convolutional neural network}

@@

	\aistatstitle{Hyperparameter Learning for Multiclass Conditional Embeddings \\ with Rademacher Complexity Bounds}

@@

		% The goal is to motivate the problem here and outline our contribution
		How can we design a scalable learning objective for learning kernel hyperparameters of conditional mean embeddings? Conditional mean embeddings are nonparametric models that encodes conditional distributions in a reproducing kernel Hilbert space directly through observed data, resulting in a flexible and powerful framework for probabilistic inference. However, their performance is greatly dependent on the choice of kernel hyperparameters and regularization, yet current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics. For conditional mean embeddings with multiclass targets but arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing datafit against model complexity. The approach only requires batch updates, allowing scalable kernel learning without kernel approximations. Experiments demonstrate that our framework outperforms standard cross validation and heuristics, and can be further extended to incorporate and learn neural network weights to improve generalization.

@@

		\Glspl{CME} are attractive because they encode conditional expectations in a \gls{RKHS}, bypassing the need for a parametrized distribution \citep{song2013kernel}. They are part of a broader class of models known as kernel embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}. This very general framework is core to modern kernel probabilistic methods, including kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery \citep{jitkrittum2016interpretable}, and state space filtering \citep{kanagawa2016filtering}.

@@

		% % In this paper, we focus on a rarely investigated form of the CME...
		\Glspl{MCE} are \glspl{CME} with discrete targets but arbitrary inputs, where on top of conditional expectations we can further infer conditional probabilities. As such, they are widely applicable to probabilistic inference in multiclass settings and learning probabilistic representations between arbitrary inputs and a discrete set of actions or outcomes. Unlike \glspl{SVM} \citep{scholkopf2002learning}, \glspl{GPC} \citep{rasmussen2006gaussian}, and multiclass \glspl{RLSC} \citep{rifkin2003regularized, pahikkala2012unsupervised}, \Glspl{MCE} do not require separately fitting binary classifiers for each class or each pair of classes for a final multiclass prediction. Instead, a single conditional embedding is sufficient for producing consistent multiclass probabilistic estimates.

@@

		One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which has long enjoyed the well celebrated marginal likelihood for hyperparameter learning. The marginal likelihood arises naturally from the Bayesian formulation of the model, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity. On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond unseen examples.

@@

		Can we formulate a learning objective for \glspl{MCE} that resembles the marginal likelihood of \gls{GPs} to balance data fit and model complexity? In this paper, we present such a learning objective as our main contribution. In particular, we 1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, 2) formulate a novel learning objective based on this complexity measure to control expected generalization risk by balancing data fit against model complexity, and 3) propose a scalable hyperparameter learning algorithm under this objective using batch updates. We show that this learning objective produces \glspl{MCE} that generalizes better than that learned from cross validation, \gls{ERM}, and median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights to improve generalization accuracy on the MNIST dataset. % Finally, we also discuss some variations to the \gls{MCE} model.

@@

			Under the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, it can be shown that $\mathcal{U}_{Y | X} = C_{YX} C_{XX}^{-1}$. While this assumption is satisfied for finite domains $\mathcal{X}$ with a characteristic kernel $k$, it does not necessarily hold when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the case for many classification problems. In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularize the inversion and use $\mathcal{U}_{Y | X} = C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep{song2013kernel}. \glspl{CME} are useful for probabilistic inference as conditional expectations of a function $g \in \mathcal{H}_{l}$ can be expressed as inner products, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$, provided $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert}.

@@

			Hyperparameter learning for conditional embeddings is particularly difficult compared to marginal or joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularization parameter $\lambda \in \Lambda = \mathbb{R}_{+}$. \cite{lever2012conditional} showed that $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to the regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$, 
			\begin{equation}
				\hat{\mathcal{E}}_{n, \lambda}[\mathcal{U}] = \frac{1}{n} \sum_{i = 1}^{n} \big\| l(y_{i}, \cdot) - \mathcal{U} k(x_{i}, \cdot) \big\|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}.
			\label{eq:lever_objective}
			\end{equation}
			Minimizing this objective directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ and $k = k_{\theta}$ would result in an overfitted model with small $\lambda$. This illustrates that the notion of model complexity during learning is especially important to ensure good generalization. \cite{lever2012conditional} proposes to hold out a validation set $\{k(x_{t_{j}}, \cdot), l(y_{t_{j}}, \cdot)\}_{j = 1}^{J}$ and minimize $\frac{1}{J} \sum_{j = 1}^{J} \big\| l(y_{t_{j}}, \cdot) - \hat{\mathcal{U}}_{Y | X} k(x_{t_{j}}, \cdot) \big\|_{\mathcal{H}_{l}}^{2}$ where $\hat{\mathcal{U}}_{Y | X}$ is estimated from the remaining training set using \eqref{eq:empirical_conditional_embedding}. This could also be repeated over multiple folds for cross validation. \cite{song2013kernel} also uses this cross validation approach, but includes $\lambda \| \mathcal{U} \|_{HS}$ in the minimization. This approach improves generalization of \glspl{CME} to unseen examples. However, they require the selection for the split and number of folds, and are not optimized for any particular prediction task. By fitting a separate model for each fold during learning, they also incur a large computational cost of $O(J n^{3})$ for $J$ folds, and becomes prohibitive with large datasets.

			When cross validation is too expensive, for many stationary kernels, the length scale parameter can be set by the median heuristic \citep{muandet2016kernel} via $\ell = \mathrm{median}_{i, j}(\| x_{i} - x_{j} \|_{2})$. However, they are restricted to length scale parameters only and cannot be used to set other hyperparameters, such as $\lambda$. In the setting of two sample testing, \cite{gretton2012optimal} also notes that they can possibly lead to poor performance. In the context of \glspl{CME}, they also do not take into account of labeled information. \cite{flaxman2016bayesian} proposed a Bayesian learning framework for marginal embeddings via inducing points, though it is unclear how this can be extended to include \glspl{CME}. \cite{fukumizu2009kernel} also investigated the choice of kernel bandwidth for stationary kernels in the setting of binary classification and two sample testing using the \gls{MMD}, but has yet to generalize to \glspl{CME} or multiclass settings.

@@

			In many cases, learning is usually done by minimizing some empirical loss over a class of models whose Rademacher complexity is bounded. For a linear class of predictors parametrized as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds in the context of multi-label learning. \cite{xu2016local} extends the trace norm regularization approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimize the tail sum of the predictor singular values. Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for \glspl{SVC}. Similarly, \cite{pontil2013excess} also used trace norm regularization to bound the Rademacher complexity and minimizes the truncated hinge loss. Nevertheless, while Rademacher complexities have been employed to restrict the function class considered for learning weight parameters of linear models, they are usually not minimized along with the loss and have not yet been applied to learn hyperparameters.

@@

		In particular, the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ is on the input kernel $k$ not the output kernel $l$, which is a Kronecker delta $l = \delta$ for \glspl{MCE}. In practice, this assumption can be relaxed through introducing the regularization parameter $\lambda$ as in \eqref{eq:empirical_conditional_embedding} \citep{song2009hilbert}.

		While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalized distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size. When normalized distributions are required, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalized,
		\begin{equation}
		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
		\label{eq:empirical_decision_probability_clip_normalised}
		\end{equation}
		Of course, classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.  \Cref{thm:probability_convergence_copy} also implies the reducing effect of clip-normalisation as with increasing sample sizes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$.

		Similar to \gls{RLSC}, \glspl{MCE} are solutions to a regularized least squares problem in a \gls{RKHS} \citep{lever2012conditional}, resulting in a similar system of linear equations. \glspl{RLSC} primarily differ in the way they handle the labels, in which binary labels $\{-1, 1\}$ appear directly in the squared loss instead of its kernel representation $\delta(y_{i}, \cdot)$ or, equivalently, its one hot encoded form $\bvec{y}_{i}$. Consequently, multiclass extensions for \gls{RLSC} either require using the \gls{OVA} scheme \citep{rifkin2003regularized}, or minimizing the summed losses across all binarized tasks instead \citep{pahikkala2012unsupervised}, producing separate classifiers for each class. As a result, multiclass \gls{RLSC} do not produce consistent estimates of class probabilities as in \cref{thm:probability_convergence_copy} for \glspl{MCE}. This property allows us to employ a probabilistic loss over the output of \glspl{MCE} to learn its hyperparameters, which is known to be difficult to tune in the case of \gls{RLSC} \citep{pahikkala2012unsupervised}. However, simply minimizing the empirical loss could lead to overfitting due to the flexibility of the nonparametric model. It is therefore essential to control the model complexity of \glspl{MCE}, which we turn to next.

@@

		\begin{algorithm*}[tb]
			\caption{\gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
			\label{alg:multiclass_conditional_embedding_training}
			\begin{algorithmic}[1]
				\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
				\REPEAT
				\STATE Sample the next batch $\mathcal{I}_{b} \subseteq \mathbb{N}_{n}$, $| \mathcal{I}_{b} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I}_{b} = \mathbb{N}_{n}$)
				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}_{b}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
				\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}_{b}, j \in \mathcal{I}_{b}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
				\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
				\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i = 1}^{n_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
			\end{algorithmic}
		\end{algorithm*}

		In order to design a hyperparameter learning algorithm that maximizes generalization performance without overfitting, we begin by defining a loss function as a measure for performance. For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ the cross entropy loss,
		\begin{equation}
		\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
		\label{eq:cross_entropy_loss_copy}
		\end{equation}
		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$. Note that we employ the loss on the raw probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clipped version \eqref{eq:empirical_decision_probability_clip_normalised}. Under this loss, we prove that the expected risk for the \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a \gls{RCB} $r(\theta, \lambda)$ with high probability.

		\begin{theorem}[Expected Risk Bound for \gls{MCE} Hyperparameter Learning]
			\label{thm:expected_risk_bound_hyperparameter_learning_copy}

>>>>

\newacronym{CME}{CME}{conditional mean embedding}
\newacronym{MCE}{MCE}{multiclass conditional embedding}
\newacronym{CEN}{CEN}{conditional embedding network}
\newacronym{RKHS}{RKHS}{reproducing kernel Hilbert space}
\newacronym{SVM}{SVM}{support vector machine}
\newacronym{SVC}{SVC}{support vector classifier}
\newacronym{GP}{GP}{Gaussian process}
\newacronym{GPs}{GPs}{Gaussian processes}
\newacronym{GPC}{GPC}{Gaussian process classifier}
\newacronym{KRR}{KRR}{kernel ridged regressor}
\newacronym{RLSC}{RLSC}{regularized least squares classifier}
\newacronym{ERM}{ERM}{empirical risk minimization}
\newacronym{MMD}{MMD}{maximum mean discrepancy}
\newacronym{RCB}{RCB}{Rademacher complexity bound}
\newacronym{OVA}{OVA}{one versus all}
\newacronym{CNN}{CNN}{convolutional neural network}
\newacronym{ARD}{ARD}{automatic relevance determination}
\newacronym{HS}{HS}{Hilbert-Schmidt}

@@

	\aistatstitle{Hyperparameter Learning for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds}

@@

		% The goal is to motivate the problem here and outline our contribution
		How can we design a scalable learning objective for learning kernel hyperparameters of conditional mean embeddings? Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space directly through observed data, resulting in a flexible and powerful framework for probabilistic inference. However, their performance is greatly dependent on the choice of kernel hyperparameters and regularization, yet current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics. For conditional mean embeddings with categorical targets but arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity. The approach only requires batch updates, allowing scalable kernel learning without kernel approximations. Experiments demonstrate that our framework outperforms standard cross validation, and can be further extended to incorporate and learn neural network weights improving generalization.

@@

		\Glspl{CME} are attractive because they encode conditional expectations in a \gls{RKHS}, bypassing the need for a parametrized distribution \citep{song2013kernel}. They are part of a broader class of models known as kernel embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}. This very general framework is core to modern kernel probabilistic methods, including kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, density estimation \citep{song2008tailoring, kanagawa2014recovering}, component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery \citep{jitkrittum2016interpretable}, and state space filtering \citep{kanagawa2016filtering}.

@@

		% % In this paper, we focus on a rarely investigated form of the CME...
		For \glspl{CME} with categorical targets but arbitrary inputs, we can further infer conditional probabilities directly, and not just conditional expectations. As there can be more than two categories, we refer to these \glspl{CME} as \glspl{MCE} in this paper. In contrast, \glspl{SVM} \citep{scholkopf2002learning} do not naturally produce probabilities, while \glspl{GPC} \citep{rasmussen2006gaussian} require posterior approximations. As such, \glspl{MCE} are widely applicable to probabilistic inference in multiclass settings with categorical targets. Unlike \glspl{SVM}, \glspl{GPC}, and multiclass \glspl{RLSC} \citep{rifkin2003regularized, pahikkala2012unsupervised}, \glspl{MCE} do not require separately fitting multiple binary classifiers to obtain a final prediction. Instead, a single \gls{MCE} is sufficient for producing consistent multiclass probabilistic estimates.

@@

		One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which have long enjoyed the well celebrated marginal likelihood for hyperparameter learning. The marginal likelihood arises naturally from the Bayesian formulation of \gls{GPs}, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity. On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond unseen examples.

@@

		Can we formulate a learning objective for \glspl{MCE} that resembles the marginal likelihood of \gls{GPs} to balance data fit and model complexity? In this paper, we present such a learning objective as our main contribution. In particular, we (1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, (2) formulate a novel learning objective based on this complexity measure to control expected generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates. We show that this learning objective produces \glspl{MCE} that generalizes better than that learned from cross validation, \gls{ERM}, and median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy. % Finally, we also discuss some variations to the \gls{MCE} model.

@@

			Under the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, it can be shown that $\mathcal{U}_{Y | X} = C_{YX} C_{XX}^{-1}$. While this assumption is satisfied for finite domains $\mathcal{X}$ with a characteristic kernel $k$, it does not necessarily hold when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the case for many classification problems. In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularize the inversion and use $\mathcal{U}_{Y | X} = C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep{song2013kernel}. \glspl{CME} are useful for probabilistic inference as conditional expectations of a function $g \in \mathcal{H}_{l}$ can be expressed as inner products, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$, provided that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ \citep[Theorem 4]{song2009hilbert}.

@@

			Hyperparameter learning for conditional embeddings is particularly difficult compared to marginal or joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularization parameter $\lambda \in \Lambda = \mathbb{R}_{+}$. \cite{lever2012conditional} showed that $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to the regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$, 
			\begin{equation}
				\hat{\mathcal{E}}_{n, \lambda}[\mathcal{U}] = \frac{1}{n} \sum_{i = 1}^{n} \big\| l(y_{i}, \cdot) - \mathcal{U} k(x_{i}, \cdot) \big\|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|^{2}_{HS}.
			\label{eq:lever_objective}
			\end{equation}
			Minimizing this objective directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ and $k = k_{\theta}$ would result in an overfitted model with small $\lambda$. This illustrates that the notion of model complexity during learning is especially important to ensure good generalization. \cite{lever2012conditional} proposes to hold out a validation set $\{k(x_{t_{j}}, \cdot), l(y_{t_{j}}, \cdot)\}_{j = 1}^{J}$ and minimize $\frac{1}{J} \sum_{j = 1}^{J} \big\| l(y_{t_{j}}, \cdot) - \hat{\mathcal{U}}_{Y | X} k(x_{t_{j}}, \cdot) \big\|_{\mathcal{H}_{l}}^{2}$ where $\hat{\mathcal{U}}_{Y | X}$ is estimated from the remaining training set using \eqref{eq:empirical_conditional_embedding}. This could also be repeated over multiple folds for cross validation. \cite{song2013kernel} also uses this cross validation approach, but includes $\lambda \| \mathcal{U} \|^{2}_{HS}$ in the minimization. This approach improves generalization of \glspl{CME} to unseen examples. However, they require the selection for the split and number of folds, and are not optimized for any particular prediction task. By fitting a separate model for each fold during learning, they also incur a large computational cost of $O(J n^{3})$ for $J$ folds, and becomes prohibitive with large datasets.

			When cross validation is too expensive, the length scale parameter can be set by the median heuristic \citep{muandet2016kernel} via $\ell = \mathrm{median}_{i, j}(\| x_{i} - x_{j} \|_{2})$ for many stationary kernels. However, they cannot be used to set hyperparameters other than length scales, such as $\lambda$. In the setting of two sample testing, \cite{gretton2012optimal} also notes that they can possibly lead to poor performance. In the context of \glspl{CME}, they also do not take into account of labeled information. \cite{flaxman2016bayesian} proposed a Bayesian learning framework for marginal embeddings via inducing points, though it is unclear how this can be extended to include \glspl{CME}. \cite{fukumizu2009kernel} also investigated the choice of kernel bandwidth for stationary kernels in the setting of binary classification and two sample testing using the \gls{MMD}, but has yet to generalize to \glspl{CME} or multiclass settings.

@@

			In many cases, classifiers are trained by minimizing some empirical loss over a class of models whose Rademacher complexity is bounded. For a linear predictors parametrized as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds in the context of multi-label learning. \cite{xu2016local} extends the trace norm regularization approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimize the tail sum of the predictor singular values. Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for \glspl{SVC}. Similarly, \cite{pontil2013excess} also used trace norm regularization to bound the Rademacher complexity and minimizes the truncated hinge loss. Nevertheless, while Rademacher complexities have been employed to restrict the function class considered for training weight parameters, they are usually not minimized along with the loss and have not yet been applied to learn hyperparameters.

@@

		In particular, the assumption $k(x, \cdot) \in \mathrm{image}(C_{XX})$ is on the input kernel $k$, not the output kernel $l$, which is a Kronecker delta $l = \delta$ for \glspl{MCE}. In practice, this assumption can be relaxed through introducing the regularization parameter $\lambda$ as in \eqref{eq:empirical_conditional_embedding} \citep{song2009hilbert}.

		While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalized distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size. When normalized distributions are required, clip-normalized estimates can be used \eqref{eq:empirical_decision_probability},
		\begin{equation}
		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
		\label{eq:empirical_decision_probability_clip_normalized}
		\end{equation}
		Classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.  \Cref{thm:probability_convergence_copy} also implies that eventually the effect of clip-normalization vanishes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$ with increasing sample sizes.

		Similar to \gls{RLSC}, \glspl{MCE} are solutions to a regularized least squares problem in a \gls{RKHS} \citep{lever2012conditional}, resulting in a similar system of linear equations. \glspl{RLSC} primarily differ in the way they handle the labels, in which binary labels $\{-1, 1\}$ appear directly in the squared loss instead of its kernel representation $\delta(y_{i}, \cdot)$ or, equivalently, its one hot encoded form $\bvec{y}_{i}$. Consequently, multiclass extensions for \gls{RLSC} either require using the \gls{OVA} scheme \citep{rifkin2003regularized}, or minimizing the summed losses across all binarized tasks instead \citep{pahikkala2012unsupervised}, producing separate classifiers for each class. As a result, multiclass \gls{RLSC} do not produce consistent estimates of class probabilities as in \cref{thm:probability_convergence_copy} for \glspl{MCE}. This property allows us to employ a probabilistic loss over the output of \glspl{MCE} to learn its hyperparameters, which is known to be difficult to tune in the case of \gls{RLSC} \citep{pahikkala2012unsupervised}. However, simply minimizing the empirical loss could lead to overfitting due to the flexibility of the nonparametric model. It is therefore essential to control the model complexity of \glspl{MCE}.

@@

		In order to design a hyperparameter learning algorithm that maximizes generalization performance without overfitting, we begin by defining a loss function as a measure for performance. For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ the cross entropy loss,
		\begin{equation}
		\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
		\label{eq:cross_entropy_loss_copy}
		\end{equation}
		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$. Note that we employ the loss on the raw probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clipped version \eqref{eq:empirical_decision_probability_clip_normalized}.

		\cite{bartlett2002rademacher} showed that the expected risk can be bounded with high probability using the empirical risk and the Rademacher complexity of the loss composed with the function class. For a Lipchitz loss, \citet{ledoux2013probability} further showed that the latter can be bounded using the Rademacher complexity of the function class itself. However, the Rademacher complexity of \glspl{MCE} over all possible sets of kernel hyperparameters $\theta \in \Theta$ and regularization $\lambda \in \Lambda$ could be infinite. Moreover, it is more fruitful to quantify the model complexity for a specific set of hyperparameters $(\theta, \lambda)$, and not over all possible hyperparameters $\Theta \times \Lambda$. Since \glspl{MCE} are linear in the \gls{RKHS}, Rademacher complexities can be bounded by bounding the trace norm, similar to the case in \cite{yu2014large}. To quantify the model complexity for a specific set of hyperparameters $(\theta, \lambda)$, we consider the Rademacher complexity over all \glspl{MCE} whose trace norm is less than the chosen \gls{MCE} with hyperparameters $(\theta, \lambda)$. Since \glspl{MCE} operate in the \gls{RKHS}, we also require that the class of hyperparameters have bounded kernels with magnitude no more than that of the chosen \gls{MCE}. From this, we prove that the expected risk for a \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a \gls{RCB} $r(\theta, \lambda)$ with high probability.

		\begin{theorem}[Expected Risk Bound for a choice of \gls{MCE} Hyperparameters]
			\label{thm:expected_risk_bound_hyperparameter_learning_copy}
